Races with hyper3 objects

### 2022-06-29 inst/race3.Rmd
remove second sticker
start work on comparison with Wilcoxon Mann Whitney

>>>>

# Power test for `hyper3` objects compared with Mann-Whitney-Wilcox

First do some stuff where the null is true:

```{r,label=definepower}
wilcox_pval <- function(a,b,pa,pb){
  o <- rrace3(pn=c(a=a,b=b),ps=c(a=pa,b=pb))
  wilcox.test(which(o=='a'),which(o=='b'))$p.value
}

hyper3_pval <- function(a,b,pa,pb){
  o <- rrace3(pn=c(a=a,b=b),ps=c(a=pa,b=pb))
  equalp.test(ordervec2supp3(o))$p.value
}
```

```{r,label=dopowernulltrue,cache=TRUE}
wil_p_h0 <- replicate(100,wilcox_pval(10,10,0.5,0.5))
hyp_p_h0 <- replicate(100,hyper3_pval(10,10,0.5,0.5))
```

```{r,label=plotpvalnulltrue}
plot(ecdf(wil_p_h0),col="black")
plot(ecdf(hyp_p_h0),col="red",add=TRUE)
legend("topleft",pch=16,lty=1,col=c("black","red"),legend=c("Wilcox","hyper3"))
```

Now some stuff where the null is false:

```{r,label=dopower,cache=TRUE}
wil_p <- replicate(100,wilcox_pval(10,10,0.7,0.3))
hyp_p <- replicate(100,hyper3_pval(10,10,0.7,0.3))
```

```{r,label=plotpower}
hist(wil_p)
hist(hyp_p)
par(pty="s")
qqplot(wil_p,hyp_p,asp=1,xlim=c(0,1),ylim=c(0,1),pty="m")
abline(0,1)
qqplot(log(wil_p),log(hyp_p),asp=1,xlim=c(-6,1),ylim=c(-6,1),pty="m")
abline(0,1)
ks.test(wil_p,hyp_p)
```
